\newif \ifdraft \draftfalse
\newif \iffull \fulltrue
\newif \ifacita \acitafalse

\documentclass[10pt,conference,compsocconf]{IEEEtran}
%\usepackage{times}
\usepackage[hyphens]{url}
\usepackage{amssymb}
\usepackage{color}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{bigstrut}
%\usepackage{alg}
\usepackage[override]{cmtt}
\usepackage[nointegrals]{wasysym}
\usepackage{graphicx}
\usepackage{balance}

\ifacita
\setlength{\textfloatsep}{1em}
\else
\fi

%DIF PREAMBLE EXTENSION ADDED BY LATEXDIFF
%DIF UNDERLINE PREAMBLE
\RequirePackage[normalem]{ulem}
\RequirePackage{color}\definecolor{RED}{rgb}{1,0,0}\definecolor{BLUE}{rgb}{0,0,1}
\providecommand{\DIFadd}[1]{{\protect\color{blue}\uwave{#1}}}
\providecommand{\DIFdel}[1]{{\protect\color{red}\sout{#1}}}
%DIF SAFE PREAMBLE
\providecommand{\DIFaddbegin}{}
\providecommand{\DIFaddend}{}
\providecommand{\DIFdelbegin}{}
\providecommand{\DIFdelend}{}
%DIF FLOATSAFE PREAMBLE
\providecommand{\DIFaddFL}[1]{\DIFadd{#1}}
\providecommand{\DIFdelFL}[1]{\DIFdel{#1}}
\providecommand{\DIFaddbeginFL}{}
\providecommand{\DIFaddendFL}{}
\providecommand{\DIFdelbeginFL}{}
\providecommand{\DIFdelendFL}{}
%\newenvironment{DIFnomarkup}{}{}
%DIF END PREAMBLE EXTENSION ADDED BY LATEXDIFF

%\begin{DIFnomarkup}
\input{defs}
%\end{DIFnomarkup}

\iffull
\IEEEoverridecommandlockouts
\title{Dynamic Enforcement of Knowledge-based Security
  Policies{\Large $ ^\dagger$}\thanks{$\dagger$ University of Maryland, Department of Computer
    Science Technical Report CS-TR-4978.  This paper is an extended
    version of the paper
    of the same title appearing in the proceedings of the 24th IEEE
    Computer Security Foundations Symposium.  This version contains
    additional discussion (Appendices~\ref{appendix:concrete}
    and~\ref{appendix:flawed}, Section~\ref{sec:poly-eval}), and bits
    throughout), new and revised 
    performance experiments (Section~\ref{sec:impl} and 
    Appendix~\ref{appendix:queries}), and proofs of
    theorems (Appendices~\ref{appendix:proof1}
    and~\ref{appendix:proof2}).}}
\else
\title{Dynamic Enforcement of Knowledge-based Security Policies}
\fi
\author{\IEEEauthorblockN{Piotr Mardziel, Stephen Magill, Michael Hicks}
\IEEEauthorblockA{University of Maryland, College Park}
\and
\IEEEauthorblockN{Mudhakar Srivatsa}
\IEEEauthorblockA{IBM T.J. Watson Research Laboratory}}

\newcommand{\myparagraph}[1]{\textbf{#1}.}
\ifdraft
\newcommand{\todo}[1]{\textbf{#1}}
\definecolor{purple}{rgb}{0.8,0,0.8}
\newcommand{\sbmcomment}[1]{\textcolor{purple}{SBM -- #1}}
\newcommand{\mwh}[1]{\textcolor{blue}{MWH -- #1}}
\newcommand{\pxm}[1]{\textcolor{red}{PM -- #1}}
\newcommand{\ms}[1]{\textcolor{yellow}{MS -- #1}}
\else
\newcommand{\todo}[1]{}
\newcommand{\sbmcomment}[1]{}
\newcommand{\mwh}[1]{}
\newcommand{\pxm}[1]{}
\newcommand{\ms}[1]{}
\fi

\begin{document}

\pagestyle{plain}


\maketitle
\date{}

\begin{abstract}
% Following Simon PJ (Kent Beck, actually) abstract structure:
% 1. State the problem 
% 2. Say why it’s an interesting problem 
% 3. Say what your solution achieves 
% 4. Say what follows from your solution
  This paper explores the idea of \emph{knowledge-based security
    policies}, which are used to decide whether to answer queries over
  secret data based on an estimation of the querier's (possibly
  increased) knowledge given the results.  Limiting knowledge is the
  goal of existing information release policies that employ mechanisms
  such as noising, anonymization, and redaction.  Knowledge-based
  policies are more general: they increase flexibility by not fixing
  the means to restrict information flow.  We enforce a
  knowledge-based policy by explicitly tracking a model of a querier's
  belief about secret data, represented as a probability distribution,
  and denying any query that could increase knowledge above a given
  threshold.  We implement query analysis and belief tracking via
  abstract interpretation using a novel 
  \emph{probabilistic polyhedral} domain, whose design permits trading off
  precision with performance while ensuring estimates of a querier's
  knowledge are sound.  Experiments with our implementation show that
  several useful queries can be handled efficiently, and performance
  scales far better than would more standard implementations of
  probabilistic computation based on sampling.
\end{abstract}

\iffull
\else
\ifacita
\else
\begin{IEEEkeywords}
privacy, abstract interpretation, probabilistic polyhedron,
knowledge-based security
\end{IEEEkeywords}
\fi \fi

\input{intro}
\input{sec-overview}
\input{sec-beliefs}
\input{sec-security}
\input{sec-abstract}
\input{sec-implement}
\input{sec-related}

\section{Conclusion}
\label{sec:conc}

This paper has explored the idea of \emph{knowledge-based security
  policies}: given a query over some secret data, that query should
only be answered if doing so will not increase the querier's knowledge
above a fixed threshold.  We enforce knowledge-based policies by
explicitly tracking a model of a querier's belief about secret data,
represented as a probability distribution, and we deny any query that
could increase knowledge above the threshold.  Our denial criterion
is independent of the actual secret, so denial does not leak
information.  We implement query analysis and belief tracking via
abstract interpretation using 
\ifacita
\emph{probabilistic polyhedral} domains.
\else
novel domains of \emph{probabilistic
  polyhedra} and \emph{powersets of probabilistic polyhedra}.
\fi
Compared to typical approaches to implementing belief revision, our
implementation using this domain is more efficient and scales better.

\ifacita
\vspace*{.05in}
\begin{small}
\paragraph*{Acknowledgments}
This research was sponsored by the U.S. Army Research Laboratory and
the U.K. Ministry of Defence and was accomplished under Agreement
Number W911NF-06-3-0001. The views and conclusions contained in this
document are those of the author(s) and should not be interpreted as
representing the official policies, either expressed or implied, of
the U.S. Army Research Laboratory, the U.S. Government, the
U.K. Ministry of Defence or the U.K. Government. The U.S. and
U.K. Governments are authorized to reproduce and distribute reprints
for Government purposes notwithstanding any copyright notation hereon.
\end{small}

\else
\vspace*{.1in}
\begin{small}
\paragraph*{Acknowledgments} The authors are
grateful to Jeff Foster, Nataliya Guts, the anonymous referees, and
especially Boris K\"opf for their helpful comments on
drafts of this paper.  

This research was sponsored by the U.S. Army
Research Laboratory and the U.K. Ministry of Defence and was
accomplished under Agreement Number W911NF-06-3-0001. The views and
conclusions contained in this document are those of the author(s) and
should not be interpreted as representing the official policies,
either expressed or implied, of the U.S. Army Research Laboratory, the
U.S. Government, the U.K. Ministry of Defence or the
U.K. Government. The U.S. and U.K. Governments are authorised to
reproduce and distribute reprints for Government purposes
notwithstanding any copyright notation hereon.  Support was also
provided by National Science Foundation grants 0905419 and
0910530.
\end{small}
\fi

\bibliographystyle{IEEEtran}
\balance
\bibliography{paper}

\iffull
\input{sec-appendix}
\fi

\end{document}

