% http://mstracker.com
% Manuscript 12-313-RR
% Dynamic Enforcement of Knowledge-based Security Policies using Probabilistic Abstract Interpretation
% Mr. Piotr Mardziel piotrm@cs.umd.edu USA UMD College Park
% Dr. Stephen Magill stephen.magill@gmail.com USA UMD College Park
% Dr. Michael Hicks mwh@cs.umd.edu USA UMD College Park
% Dr. Mudhakar Srivatsa msrivats@us.ibm.com USA IBM TJ Watson

%\newif \ifdraft \drafttrue
\newif \ifdraft \draftfalse
\newif \iffullapp \fullappfalse

%\documentclass[10pt,conference,compsocconf]{IEEEtran}
\documentclass[9pt]{article}
%\usepackage{times}
\usepackage{times}
\usepackage[hyphens]{url}
\usepackage{amssymb}
\usepackage{color}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{bigstrut}
%\usepackage{alg}
\usepackage[override]{cmtt}
\usepackage[nointegrals]{wasysym}
\usepackage{graphicx}
\usepackage{balance}
\usepackage{longtable}

\input{defs}

%\IEEEoverridecommandlockouts
\title{Dynamic Enforcement of Knowledge-based Security Policies using
  Probabilistic Abstract Interpretation}

\author{
Piotr Mardziel$^\dagger$, Stephen Magill, Michael Hicks$^\dagger$, Mudhakar
Srivatsa$^\star$\\\\
$^\dagger$ University of Maryland, College Park\\
$^\star$ IBM T.J. Watson Research Laboratory\\
}

\newcommand{\myparagraph}[1]{\textbf{#1}.}
\ifdraft
\newcommand{\todo}[1]{\textbf{#1}}
\definecolor{purple}{rgb}{0.8,0,0.8}
\definecolor{dgreen}{rgb}{0.0,0.5,0.0}
\newcommand{\sbmcomment}[1]{\textcolor{purple}{SBM -- #1}}
\newcommand{\mwh}[1]{\textcolor{blue}{MWH -- #1}}
\newcommand{\pxm}[1]{\textcolor{red}{PM -- #1}}
\newcommand{\changed}[1]{\textcolor{dgreen}{#1}}
\newcommand{\ms}[1]{\textcolor{yellow}{MS -- #1}}
\else
\newcommand{\changed}[1]{#1}
\newcommand{\todo}[1]{}
\newcommand{\sbmcomment}[1]{}
\newcommand{\mwh}[1]{}
\newcommand{\pxm}[1]{}
\newcommand{\ms}[1]{}
\fi

\begin{document}

\pagestyle{plain}

\maketitle
\date{}

%Piotr Mardziel - University of Maryland, College Park
%Stephen Magill
%Michael Hicks - University of Maryland, College Park
%Mudhakar Srivatsa - IBM T.J. Watson Research Laboratory

\begin{abstract}
% Following Simon PJ (Kent Beck, actually) abstract structure:
% 1. State the problem 
% 2. Say why it’s an interesting problem 
% 3. Say what your solution achieves 
% 4. Say what follows from your solution

  This paper explores the idea of \emph{knowledge-based security
    policies}, which are used to decide whether to answer queries over
    secret data based on an estimation of the querier's (possibly
    increased) knowledge given the results.  Limiting knowledge is the
    goal of existing information release policies that employ
    mechanisms such as noising, anonymization, and redaction.
    Knowledge-based policies are more general: they increase
    flexibility by not fixing the means to restrict information flow.
    We enforce a knowledge-based policy by explicitly tracking a model
    of a querier's belief about secret data, represented as a
    probability distribution, and denying any query that could
    increase knowledge above a given threshold.  We implement query
    analysis and belief tracking via abstract interpretation, which allows us to
    trade off precision and performance through the use of
    abstraction. We have developed an approach to augment standard
    abstract domains to include probabilities, and thus define
    distributions.  We focus on developing \emph{probabilistic
      polyhedra} in particular, to support numeric programs. While
    probabilistic abstract interpretation has been 
    considered before, our domain is the first whose design supports
    sound conditioning, which is required to ensure that estimates of
    a querier's knowledge are accurate. Experiments with our
    implementation show that several useful queries can be handled
    efficiently, particularly compared to exact (i.e., sound)
    inference involving sampling.  We also show that, for our
    benchmarks, restricting constraints to \emph{octagons}
    or \emph{intervals}, rather than full polyhedra, can dramatically
    improve performance while incurring little to no loss in
    precision.
\end{abstract}

\input{sec-intro}
\input{sec-overview}
\input{sec-beliefs}
\input{sec-security}
\input{sec-abstract}
\input{sec-implement}
\input{sec-related}

\section{Conclusion}
\label{sec:conc}

This paper has explored the idea of \emph{knowledge-based security
  policies}: given a query over some secret data, that query should
only be answered if doing so will not increase the querier's knowledge
above a fixed threshold.  We enforce knowledge-based policies by
explicitly tracking a model of a querier's belief about secret data,
represented as a probability distribution, and we deny any query that
could increase knowledge above the threshold.  Our denial criterion is
independent of the actual secret, so denial does not leak information.
We implement query analysis and belief tracking via abstract
interpretation using domains of \emph{powersets of probabilistic
polyhedra, octagons, and intervals}.
%
Compared to typical approaches to implementing belief revision, our
implementation using this domain is more efficient and scales better.

\vspace*{.1in}
\begin{small}
\paragraph*{Acknowledgments} The authors are
grateful to Jeff Foster, Nataliya Guts, the CSF'11 anonymous referees, and
especially Boris K\"opf for their helpful comments on
drafts of this paper.  

This research was sponsored by the U.S. Army
Research Laboratory and the U.K. Ministry of Defence and was
accomplished under Agreement Number W911NF-06-3-0001. The views and
conclusions contained in this document are those of the author(s) and
should not be interpreted as representing the official policies,
either expressed or implied, of the U.S. Army Research Laboratory, the
U.S. Government, the U.K. Ministry of Defence or the
U.K. Government. The U.S. and U.K. Governments are authorised to
reproduce and distribute reprints for Government purposes
notwithstanding any copyright notation hereon.  Support was also
provided by National Science Foundation grants 0905419 and
0910530.
\end{small}

\bibliographystyle{plain}
\balance
\bibliography{paper}

\input{sec-appendix}

\end{document}
